---
title: "EffOff Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{EffOff Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(EffOff)
library(sf)
library(ggplot2)
```

# Introduction

Efficacy of Forest Offsets in India under the CAMPA program, or package `EffOff` automates the analysis workflow for assessing vegetation trends in CAMPA sites using Google Earth Engine (GEE) and statistical trend analysis. This vignette demonstrates how to use the package to extract EVI data, process it, analyze trends, and visualize the results.

# 1. Data Extraction

First, we load a shapefile representing our region of interest. This can be formattted as a shapefile (.shp) or a KML (.kml)

```{r eval=FALSE}
# Load shapefile
roi <- st_read("path/to/your/shapefile.shp")

# Initialize GEE (requires authentication)
# rgee::ee_Initialize()

# Extract EVI data
# This will pull data from Landsat 5, 7, and 8, harmonized.
evi_data <- extract_evi(roi, start_year = 1990, end_year = 2024)
```

# 2. Data Processing

Clean the data by filtering invalid values, handling sensor overlaps (LS8 > LS5 > LS7), and filling gaps.

```{r eval=FALSE}
# Clean and fill gaps
cleaned_data <- clean_evi_data(evi_data)

# Calculate Annual and Seasonal Means
means <- calculate_means(cleaned_data)
annual_means <- means$AM
dry_means <- means$ADM
wet_means <- means$AWM
```

# 3. Trend Analysis

Run statistical tests: BFAST (Breakpoints), ShapeSelectForest (Trend Shape), and Mann-Kendall (Significance).

```{r eval=FALSE}
# Analyze trends on Annual Means
results <- analyze_trends(annual_means)

# View results
head(results)
```

# 4. Visualization

Visualize the results using maps and summary plots.

```{r eval=FALSE}
# Join results back to spatial data for mapping
results_sf <- roi %>%
  left_join(results, by = "PixID")

# Plot Trend Map
plot_trend_map(results_sf, variable = "SSF_Shape", title = "Vegetation Trend Shapes (1990-2024)")

# Plot Trend Summary
plot_trend_summary(results, category_col = "SSF_Shape")
```

