---
title: "EffOff Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{EffOff Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(EffOff)
library(sf)
library(ggplot2)
```

# Introduction

Efficacy of Forest Offsets in India under the CAMPA program, or package `EffOff` automates the analysis workflow for assessing vegetation trends in CAMPA sites using Google Earth Engine (GEE) and statistical trend analysis. This vignette demonstrates how to use the package to extract EVI data, process it, analyze trends, and visualize the results.

# 1. Data Extraction

First, we load a shapefile representing our region of interest. This can be formattted as a shapefile (.shp) or a KML (.kml)

```{r eval=FALSE}
# Load shapefile
roi <- st_read("path/to/your/shapefile.shp")

# Initialize GEE (requires authentication)
# rgee::ee_Initialize()

# Extract full-history EVI data
# This will pull data from 1990 to present by default.
evi_data <- extract_evi(roi)
```

# 2. Data Processing

Clean the data by filtering invalid values, handling sensor overlaps (LS8 > LS5 > LS7), and filling gaps.

```{r eval=FALSE}
# Clean and fill gaps
cleaned_data <- clean_evi_data(evi_data)

# Calculate Annual and Seasonal Means
means <- calculate_means(cleaned_data)
annual_means <- means$AM
dry_means <- means$ADM
wet_means <- means$AWM
```

# 3. Trend Analysis

Run statistical tests against a distinct project timeline. Providing a `project_start_year` and `project_end_year` splits the data into Pre-management, Management, and Post-management periods automatically. 

The analytical engine leverages three interconnected models cleanly:
- **Mann-Kendall Autocorrelation**: Uses `modifiedmk::mmkh` to compute `Tau`, `Sen's Slopes`, and `p-values` fully corrected for temporal variance structure rigorously.
- **Dynamic Breakpoints**: Employs adaptive formulas via `strucchange` and `BFAST` gracefully scaling regressors (`y~1`, `y~t`, harmonic) to bypass mathematical segment crashing on extremely short intervention datasets flawlessly.
- **Concordance Mapping**: Computes explicit structural/continuous alignment grids internally mapping across `Agreement_Triple`.

```r
# Analyze trends on Annual Means
results_list <- analyze_trends(annual_means, project_start_year = 2005, project_end_year = 2012)

# View the generated periods
names(results_list)
# e.g., "Pre_Management", "Management", "Post_Management", "Full_Intervention", "Overall", "Transitions"
```

# 4. Visualization

Visualize the results cleanly through dynamic maps and summary indices directly via `ggplot2`. A list of spatial results can be automatically rendered into structured HTML frameworks seamlessly.

```r
# Plot trend map for the entire Management period
mgmt_sf <- results_list$Management
plot_trend_map(mgmt_sf, variable = "SSF_Shape_Constrained", title = "Vegetation Trend Shapes")

# Analyze indicator agreement natively tracking Concordance mappings:
plot_trend_map(mgmt_sf, variable = "Agreement_Triple", title = "Full Agreement Between Tau, Sen, and SSF")

# Produce the complete automated HTML breakdown explicitly reporting all dimensions cleanly:
visualize(results_list)
```

