---
title: "`r params$title`"
author: "`r params$author`"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    number_sections: true
    dev: png
params:
  results_sf: NULL
  roi_sf: NULL
  reportType: "full"
  title: "Trend Analysis Report"
  author: "EffOff Package"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 7.5, fig.height = 5, dev = "png", dpi = 300) # Optimized for A4 printing
library(ggplot2)
library(sf)
library(dplyr)
library(patchwork)
library(ggspatial)
# Load the package itself to access plotting functions if not loaded
# library(EffOff)
```

# Introduction

This report presents the analysis of vegetation trends using the **EffOff** package.

```{r check-data}
if (is.null(params$results_sf)) {
    stop("Result data (results_sf) is missing.")
}
```

```{r study-area, eval=params$reportType %in% c("full", "maps")}
```

# Study Area

This section visualizes the Region of Interest (ROI) and the analysis grid.

```{r study-area-map, eval=params$reportType %in% c("full", "maps")}
# Use user provided logic for map
if (!is.null(params$roi_sf)) {
    # Check for required columns for the specific labels requested by user
    # "State", "Division", "Range", "StYP_AV", "EnYP_AV", "uid"
    required_cols <- c("State", "Division", "Range", "StYP_AV", "EnYP_AV", "uid")
    has_cols <- all(required_cols %in% names(params$roi_sf))

    # Prepare ROI sf (ensure CRS 4326 for plotting as per user code)
    roi_plot <- sf::st_transform(params$roi_sf, 4326)
    results_plot <- sf::st_transform(params$results_sf, 4326)

    # Create title/subtitle dynamically
    main_title <- "Study Area and Analysis Grid"
    sub_title <- ""
    caption_text <- ""

    if (has_cols) {
        # Assuming roi_sf has 1 row or we take the first one for the title context
        # Use robust extraction
        main_title <- paste0("CAMPA Site UID: ", roi_plot$uid[1])
        sub_title <- paste0("State: ", roi_plot$State[1], ", Division: ", roi_plot$Division[1], ", Range: ", roi_plot$Range[1])
        caption_text <- paste0("Management Duration: ", roi_plot$StYP_AV[1], " - ", roi_plot$EnYP_AV[1])
    } else {
        caption_text <- "Note: Some metadata columns (State, Division, etc.) were not found in ROI object."
    }

    # Plot
    p <- ggplot() +
        geom_sf(data = roi_plot, color = "red", fill = NA, linewidth = 1) + # polygon plot
        geom_sf(data = results_plot, size = 0.5, shape = 21, fill = "black", alpha = 0.5) + # csv point plot (grid)
        labs(
            x = "Longitude", y = "Latitude",
            title = main_title,
            subtitle = sub_title,
            caption = caption_text
        ) +
        annotation_scale(style = "ticks", tick_height = 0.3, width_hint = 0.06, location = "br", line_width = 0.5, text_cex = 0.5) +
        annotation_north_arrow(
            location = "br", style = north_arrow_minimal(text_size = 0, line_width = 0.5),
            height = unit(0.5, "cm"), pad_x = unit(-0.25, "cm"), pad_y = unit(0.5, "cm")
        ) +
        theme_bw()

    print(p)
} else {
    cat("Region of Interest (ROI) polygon not provided.")
}
```

```{r trends, eval=params$reportType %in% c("full", "maps", "graphs", "tables")}
```

# Trend Analysis

This section details the results of the harmonic trend analysis (BFAST, ShapeSelectForest, Mann-Kendall).

## Structural Changes (BFAST & SSF)

```{r structural-maps, eval=params$reportType %in% c("full", "maps")}
cat("### Spatial Distribution\n\n")

# Use package function plot_trend_map
# We need to ensure the function is available. If EffOff is loaded, good.
# Otherwise we might need to rely on it being exported.

p_bfast <- plot_trend_map(params$results_sf, "BFAST_Break", title = "BFAST Breakpoint Years")
p_ssf <- plot_trend_map(params$results_sf, "SSF_Shape_Constrained", title = "SSF Trend Shape (Constrained)")

print(p_bfast)
print(p_ssf)
```

```{r structural-stats, eval=params$reportType %in% c("full", "graphs", "tables")}
cat("### Statistical Summary\n\n")

p_summary_ssf <- plot_trend_summary(params$results_sf, "SSF_Shape_Constrained") +
    ggtitle("Distribution of Trend Shapes")

print(p_summary_ssf)
```

## Statistical Trends (Mann-Kendall)

```{r mk-maps, eval=params$reportType %in% c("full", "maps")}
cat("### Significance and Magnitude\n\n")

if ("MK_pVal" %in% names(params$results_sf)) {
    params$results_sf$MK_Significance <- ifelse(params$results_sf$MK_pVal < 0.05, "Significant", "Not Significant")
    p_sig <- plot_trend_map(params$results_sf, variable = "MK_Significance", title = "Mann-Kendall Significance (p < 0.05)")
    print(p_sig)
}

p_slope <- plot_trend_map(params$results_sf, "MK_SenSlope", title = "Sen's Slope (Magnitude of Trend)")
print(p_slope)
```

```{r mk-stats, eval=params$reportType %in% c("full", "graphs", "tables")}
cat("### Slope Distribution\n\n")

p_hist_slope <- plot_trend_summary(params$results_sf, "MK_SenSlope")
print(p_hist_slope)
```

# Summary

Analysis completed on `r nrow(params$results_sf)` pixels.
