---
title: "`r params$title`"
author: "`r params$author`"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M:%S')`"
output: 
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    number_sections: true
    dev: png
params:
  results_list: NULL
  results_sf: NULL
  roi_sf: NULL
  reportType: "full"
  title: "Trend Assessment Document"
  author: "EffOff Analytical Pipeline"
  name: NULL
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 7, dev = "png", dpi = 300)
library(ggplot2)
library(sf)
library(dplyr)
library(patchwork)
library(ggspatial)
# Ensure EffOff internals are loaded securely seamlessly executing nested algorithms explicitly
tryCatch(devtools::load_all(quiet = TRUE), error = function(e) {})
```

# Introduction

This document provides a systematic assessment of spatiotemporal vegetation trajectories generated by the **EffOff Package Framework**, applied to evaluate long-term ecological recovery and intervention outcomes.

The analytical process utilizes three core computational models to assess pixel-level vegetation dynamics using Landsat-derived Enhanced Vegetation Index (EVI) time series over multiple temporal periods:
1. **BFAST Lite** (Breaks For Additive Season and Trend): A breakpoint detection algorithm used to detect structural changes in vegetation. This identifies the timing of significant shifts corresponding to management interventions, disturbance events, or site preparation. Additionally, it computes spatial coherence to assess the extent to which vegetation trajectory changes occurred synchronously across the site.
2. **ShapeSelectForest (SSF)**: Fits structural trend candidate models based on the Bayesian Information Criterion (BIC). This provides insight into the long-term trajectory and sustainability of vegetation recovery by categorizing shape outputs (e.g., *Flat, Decreasing, Linear Increasing, Vee, Double Jump*).
3. **Mann-Kendall & Sen's Slope**: Applies the modified Mann–Kendall (MK) test and Sen’s slope estimator to provide robust detection of monotonic trends and estimate trend strength. It computes Sen’s slope for magnitude, Kendall’s tau ($\tau$) for direction, and z-statistics for significance ($p < 0.05$).

---

```{r provenance-eval, include=FALSE}
# Compute global provenance details
run_date <- Sys.Date()
pkg_version <- tryCatch(as.character(utils::packageVersion("EffOff")), error = function(e) "1.1.0")

proj_crs <- "N/A"
if (!is.null(params$results_list)) {
    valid_sfs <- Filter(function(x) inherits(x, "sf"), params$results_list)
    rep_results <- if (length(valid_sfs) > 0) valid_sfs[[1]] else params$results_list[[1]]
} else {
    rep_results <- params$results_sf
}

proj_crs <- tryCatch(toString(sf::st_crs(rep_results)$input), error = function(e) "Unspecified Bounds")
num_pixels <- nrow(rep_results)

projected_crs <- 3857
single_pixel_m2 <- tryCatch(
    {
        stats::median(as.numeric(sf::st_area(sf::st_transform(rep_results[1, ], projected_crs))), na.rm = TRUE)
    },
    error = function(e) 900
)

main_title <- paste0("Project Coverage Net: ", ifelse(is.null(params$name), "Analysis Output", params$name))
mgmt_duration <- "Standard Pipeline"
if (!is.null(params$roi_sf) && "uid" %in% names(params$roi_sf)) {
    main_title <- paste0("CAMPA Location Block UID: ", params$roi_sf$uid[1])
    mgmt_duration <- paste0(params$roi_sf$StYP_AV[1], " to ", params$roi_sf$EnYP_AV[1])
} else if (!is.null(params$results_list$Management)) {
    mgmt_duration <- params$results_list$Management$AnalysisDuration[1]
}
```

# Execution Provenance

* **Analysis Executed on**: `r run_date`
* **EffOff Engine Version**: `v` `r pkg_version`
* **Geographical Matrix (CRS)**: `r proj_crs`
* **Extracted Resolution Bounds**: `r round(single_pixel_m2, 0)` sq.m per target
* **Arrayed Vector Yield**: `r format(num_pixels, big.mark=",")` spatial tracking points
* **Boundary Name**: `r main_title`
* **Target Management Window**: `r mgmt_duration`
* **Evaluation Type Boundary**: `r toupper(params$reportType)`

---

```{r dynamic-loop, results='asis', echo=FALSE, warning=FALSE, message=FALSE, fig.width=14, fig.height=8}
# HTML formatting components
.render_table <- function(df, caption) {
    if (nrow(df) == 0) {
        return(NULL)
    }
    if (requireNamespace("gt", quietly = TRUE)) {
        tbl <- gt::gt(df) |>
            gt::tab_header(title = caption) |>
            gt::as_raw_html()
        return(tbl)
    } else {
        return(knitr::kable(df, caption = caption, format = "html", table.attr = "class='table table-striped'"))
    }
}

.process_phase <- function(phase_data, phase_name) {
    cat("\\newpage\n\n")
    cat("# ", stringr::str_replace_all(phase_name, "_", " "), " Evaluation Output\n\n")

    # 1. Key Findings Tabulation
    summ <- summarise_results(phase_data)
    cat("## Key Findings Matrix\n\n")

    print(.render_table(summ$continuous, "Summary Statistics"))
    cat("\n\n")

    if (nrow(summ$significance) > 0) {
        print(.render_table(summ$significance, "P-Value Confidence Matrix (<0.05)"))
        cat("\n\n")
    }

    if (nrow(summ$ssf_proportions) > 0) {
        print(.render_table(summ$ssf_proportions, "Morphological Trajectories (Proportional Distribution)"))
        cat("\n\n")
    }

    if (params$reportType == "diagnostics") {
        cat("## Diagnostics Matrix\n\n")
        plots <- plot_trend_map(phase_data, variable = "all", roi_sf = params$roi_sf, name = phase_name)
        print(plots$Panel3_Agreement)
        cat("\n\n")
        return()
    }

    # 3. Standard Graphics Loop
    cat("## Spatial Configurations\n\n")
    plots <- plot_trend_map(phase_data, variable = "all", roi_sf = params$roi_sf, name = phase_name)

    if (params$reportType %in% c("full", "maps", "graphs")) {
        cat("### Structural Shifts (BFAST) & Trend Shape Classifications (SSF)\n")
        print(plots$Panel1_Structural)
        cat("\n\n")

        cat("### Continuous Monotonic Trends (Mann-Kendall & Sen's Slope)\n")
        print(plots$Panel2_Statistical)
        cat("\n\n")

        cat("### Algorithm Concordance & Methodological Alignment\n")
        print(plots$Panel3_Agreement)
        cat("\n\n")
    }

    if (params$reportType %in% c("full", "graphs")) {
        cat("### Quantitative Distribution Summaries\n")
        print(plot_trend_summary(phase_data, category_col = "all", name = phase_name))
        cat("\n\n")
    }
}

if (!is.null(params$results_list)) {
    order_phases <- c("Pre_Management", "Management", "Post_Management", "Full_Intervention", "Overall")
    for (phase in intersect(order_phases, names(params$results_list))) {
        if (!is.null(params$results_list[[phase]])) .process_phase(params$results_list[[phase]], phase)
    }
} else if (!is.null(params$results_sf)) {
    .process_phase(params$results_sf, params$name)
}
```

```{r transitions, results='asis', echo=FALSE, warning=FALSE, message=FALSE, fig.width=10, fig.height=6}
if (!is.null(params$results_list$Transitions) && params$reportType != "diagnostics") {
    cat("\\newpage\n\n")
    cat("# Phase Change Conversions (Transitions)\n\n")
    cat("This analysis evaluates pixel-wise vegetation trend transitions between consecutive site-specific management periods (e.g., shifts from Pre-management baseline to active Management period). \n\n")

    trans_list <- params$results_list$Transitions
    for (t_name in names(trans_list)) {
        if (!is.null(trans_list[[t_name]])) {
            cat("### ", stringr::str_replace_all(t_name, "_", " "), " Evaluation Output\n\n")
            p <- plot_transition_summary(trans_list[[t_name]], name = stringr::str_replace_all(t_name, "_", " "))
            print(p)
            cat("\n\n")
        }
    }
}
```
